Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-06 sections/theoretical.tex
Added RadiovsTheoretical graph
Removed unused figure and reworded text to not need a figure reference

In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
We used the free, open-source planetarium software \texttt{Stellarium} to achieve this.
After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.

The resulting theoretical lightcurve is shown in Figure \ref{fig:livestream_stellarium_comparison}, alongside the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, validating our optical eclipse lightcurve.
% This figure should include the Livestream, Light Sensor, and Stellarium data.

@@

>>>>

In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
We used the free, open-source planetarium software \texttt{Stellarium} to achieve this.
After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
The resulting theoretical lightcurve is overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, validating our optical eclipse lightcurve.

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/RadiovsTheoretical.png}
  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
\end{figure}
